Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-09-23 manuscript/main.tex
Forecasts are not live when they are in the manuscript
Embed dynamically generated tables in manuscript
Adds a dynamically generated table summarizing model accuracy for simulated
populations and the associated pandas code in a Jupyter notebook to generate
this table. Also adds the corresponding latex code to include the table in the
appropriate environment.
Update distance-based model schematic
Simplifies the caption for this figure by removing description of weighted
distance-based model for now. This simplification also allows the new figure
mockup to fit in the correct place of the text.

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\columnwidth]{figures/distance-based-fitness-model.png}
  \caption{
    Schematic representation of the fitness model wherein the fitness of samples at timepoint $t$ is used to minimize the distance between projected samples from that timepoint and the observed population at timepoint $u$ one year in the future.
    A) A phylogeny at timepoint $u=$April 2004 shows the observed population at that timepoint.
    The vertical dashed line delineates the previous timepoint of $t=$April 2003 where the size and color of each sample indicates the projected frequency of those samples one year in the future based on the composite model of delta frequency, HI cross-immunity, and non-epitope mutations.
    Bright yellow samples indicate those with the highest projected frequency and closest to the observed future population one year in the future.
    B) The density of average distances between samples at different timepoints show how the model estimates the future population from the current population.
    The blue line indicates the distance between populations at timepoints $t$ and $u$, or the best estimate by a naive model that projects no change in sample frequencies.
    The orange line shows the distance between the observed future population at timepoint $u$ and the estimated population at that time ($\hat{u}$) produced by projecting the frequency of samples at timepoint $t$ based on estimates of sample fitness.
    The green line shows the distance between the observed future population and itself.
    Notably, the estimated future population shifts the distribution of the naive model closer to zero.
  }
  \label{fig:model}
  \end{center}
\end{figure*}

@@

@@

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/nextstrain-forecasts-for-september-2020.png}
  \caption{Live forecasts on nextstrain.org from our best model for September 2020.}
  \label{fig:nextstrain_forecasts}
  \end{center}
\end{figure*}

>>>>

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\columnwidth]{figures/distance-based-fitness-model.png}
  \caption{
    Schematic representation of the fitness model wherein the fitness of samples at timepoint $t$ is used to minimize the distance between projected samples from that timepoint and the observed population at timepoint $u$ one year in the future.
    A) A phylogeny at timepoint $u=$April 2004 shows the observed population at that timepoint.
    The vertical dashed line delineates the previous timepoint of $t=$April 2003 where the size and color of each sample indicates the projected frequency of those samples one year in the future based on the composite model of delta frequency, HI cross-immunity, and non-epitope mutations.
    Bright yellow samples indicate those with the highest projected frequency and closest to the observed future population one year in the future.
  }
  \label{fig:model}
  \end{center}
\end{figure*}

@@

\begin{table*}[h]
  \begin{center}
    \input{tables/simulated_model_selection.tex}
    \caption{Simulated population model accuracy relative to the naive model}
    \label{table_simulated_model_selection}
  \end{center}
\end{table*}

@@

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/nextstrain-forecasts-for-september-2020.png}
  \caption{Forecasts on nextstrain.org from our best model for September 2020.}
  \label{fig:nextstrain_forecasts}
  \end{center}
\end{figure*}
